---
output: html_document
title: "Julia vs R Comparison Cheat Sheet"
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = 'C:\\temp')
knitr::opts_chunk$set(echo = TRUE, cache=TRUE)
knitr::knit_engines$set(julia = JuliaCall::eng_juliacall)
knitr::knit_hooks$set(chunk = function(x, options) {
  print(options)
  if (options$engine == "R") { 
    paste0("<div class='column-left'> ", x, "</div>")
  }
  else if (options$engine == "julia") { 
    paste0("<div class='column-right'>", x, "</div>")}
  else { x }
})

```

<style>
.column-left{
  float: left;
  width: 47.5%;
  text-align: left;
}
.column-right{
  float: right;
  width: 47.5%;
  text-align: left;
}
.clear {
  clear:both;
}
</style>


## Vector

#### Row vector, 1 × n-matrix

```{r}
x <- 1:3
x
```
```{julia}
x = [1 2 3];
x
```

<div class="clear"></div>

#### Column vector, m × 1-matrix
```{r}
x <- t(1:3)
x
```
```{julia}
x = [1 2 3]';
x
```
</div>
<div class="clear">

#### Sequence Generation
```{r}
x <- seq(5, 1, by=-2)
x
```
```{julia}
x = collect(5:-2:1)
x
```
<div class="clear"></div>

#### Access to each element
```{r}
x <- 1:3
print(x[1])
x[length(x)]
```


```{julia}
x = [1 2 3];
x[1]
x[end]
```
<div class="clear"></div>


## String
```{r}
x <- "Hello, R"
x
```
```{julia}
x = "Hello, Julia";
x
```
<div class="clear">
</div>

#### Concatenate	
```{r}
x <- paste("Hello,", "R")
x
```
```{julia}
x = "Hello," * "julia";
x = string("Hello,", "julia"); 
x
```
<div class="clear">
</div>

#### Replicate
```{r}
x <- paste(rep('a', 3), collapse='')
x
```
```{julia}
x = repeat("a", 3);
x = 'a'^3;
x
```
<div class="clear">
</div>


#### Length
```{r}
x <- "abcde"
stringr::str_length(x)
```
```{julia}
x = "abcde";
length(x)
```
<div class="clear">
</div>

#### contain/detect
```{r}
stringr::str_detect("Hello, world.", "world")
```
```{julia}
contains("Hello, world.", "world")
```
<div class="clear">
</div>

#### collapse into a single string/join
```{r}
x <- c("apples", "bananas", "pineapples")
paste(x, collapse = ", ")
```
```{julia}
x = ["apples", "bananas", "pineapples"];
join(x, ", ")
```
<div class="clear">
</div>

#### Format and interpolate a string
```{r}
x <- "Hello, world"
glue::glue("{x}")
```
```{julia}
x = "Hello, world";
"$x"
```
<div class="clear">
</div>


## Function
```{r}
f <- function(x){x+1}
f(1)
```
```{julia}
function f(x)
  x + 1
end;
f(1)
f(x) = x + 1;
f(1)
```
<div class="clear">
</div>

#### Anonymous function
```{r}
(function(x){x+1})(1)
```
```{julia}
(x -> x + 1)(1)
```
<div class="clear">
</div>

#### Show function content
```{r}
f <- function(x){
  x + 1
}
f
```
```{julia}
function f(x)
  x + 1
end;
# less(f, (Number,)) not in REPL environment
# See https://stackoverflow.com/a/26226605/3926333
code_typed(f, (Number,))
```
<div class="clear">
</div>

## Types
```{r}
x <- 1
class(x)
```
```{julia}
x = 1;
typeof(x)
```
<div class="clear">
</div>

## Dealing with NA (missing)
```{r}
x <- c(1,2,NA,5)
sum(x, na.rm = TRUE)
```
```{julia}
# not yet in v0.6.2
#x = [1, 2, missing, 5];
#sum(skipmissing(x))
```
<div class="clear">
</div>


## Set and get working directory
```{r}
setwd("C:\\temp")
```

```{julia}
cd("C:\\temp")
```

```{r}
getwd()
```

```{julia}
pwd()
```
